\documentclass[a5paper, 12pt, openany]{memoir}

\input stdsetup

\grechangestyle{translation}{\inglesh \fontsize{9}{11}\selectfont}
\renewcommand\tr[1]{\selectlanguage{british}{\inglesh \fontsize{9}{11}\selectfont #1}}

\begin{document}

\mytitle{Ad Tertiam}{The Third Hour --- Mid-morning}

\tableofcontents*

\input deus-memento


%Tone 8G

\chapter{Psalmody}

\gregorioscore{gabc/an--maria_virgo_assumpta_est--vatican-init}

\subsection{Psalm 119}

\gresetinitiallines0
\gregorioscore{gabc/119-8}

%Ad Dóminum cum tribulárer cla\textbf{má}vi, * et \textit{exau}\textbf{dí}vit me.

% Next psalm just uses blank lines between lines.

%\input gabc/119-8

\setcounter{versecount}{2}
\startParallel
\input psalms/119-8-engl
\stopParallel


\subsection{Psalm 120}

\gregorioscore{gabc/120-8}

%Levávi óculos meos in \textbf{mon}tes, * unde véniet auxí\textit{lium} \textbf{mi}hi.

\setcounter{versecount}{2}
\startParallel
\input psalms/120-8-engl
\stopParallel


\subsection{Psalm 121}

\gregorioscore{gabc/121-8}

%Laetatus sum in his quae dicta sunt mihi~: In domum Domini ibimus.

\setcounter{versecount}{2}
\startParallel
\input psalms/121-8-engl
\stopParallel


\gregorioscore{gabc/an--maria_virgo_assumpta_est--vatican}

\gresetinitiallines1
\chapter{Little Chapter}
\label{littlechapter}

\gregorioscore{chapter-et-sic-engl}

\setcounter{versecount}{0}
%\startParallel
%Et sic in Sion firmáta sum, et in civitáte sanctificáta simíliter requiévi, et in Jerúsalem potéstas mea.
%\switchcolumn
%\tr{And in this way, I was established in Zion. And likewise, in the holy city, I found rest.
%And my authority was in Jerusalem.}
%\switchcolumn*
%R. Deo grátias.
%\switchcolumn
%\tr{Thanks be to God.}
%\stopParallel


\bigskip

\gresetinitiallines0
\gregorioscore{versicle-diffusa-engl}

\gresetinitiallines1
%\startParallel
%\versicle Diffúsa est grátia in lábiis tuis.

%\response Proptérea benedíxit te Deus in aetérnum.
%\switchcolumn
%\tr{V. Grace is poured into thy lips.}

%\tr{R. Therefore God hath blessed thee for ever.}
%\stopParallel


\chapter{The End}


\startParallel
\versicle Dómine, exáudi oratiónem meam.

\response Et clamor meus ad te véniat.

Orémus

\switchcolumn
\tr{O Lord, hear my prayer.

    And let my cry come unto Thee.

    Let us pray.}
\switchcolumn*
Deus, qui salútis ætérnæ, beátæ Maríæ virginitáte fecúnda, humáno géneri prǽmia præstitísti: tríbue, quǽsumus; ut ipsam pro nobis intercédere sentiámus, per quam merúimus auctórem vitæ suscípere, Dóminum nostrum Jesum Christum Fílium tuum:
Qui tecum vivit et regnat in unitáte Spíritus Sancti, Deus, per ómnia sǽcula sæculórum.

\response Amen.
\switchcolumn
\tr{O God, Who, by the fruitful virginity of the Blessed Mary, hast given unto mankind the rewards of everlasting life; grant, we beseech thee, that we may continually feel the might of her intercession through whom we have worthily received the Author of our life, our Lord Jesus Christ, thy Son:
    Who with thee liveth and reigneth, in the unity of the Holy Spirit, one God, world without end.
    R. Amen}
\switchcolumn
\versicle Dómine, exáudi oratiónem meam.

\response Et clamor meus ad te véniat.

\stopParallel


%\section{Conclusion}

\

\gresetinitiallines0
\gregorioscore{gabc/BenedicamusDomino}

%\versicle Benedicámus Dómino.

%\response Deo grátias.

\

\versicle Fidélium ánimæ per misericórdiam Dei requiéscant in pace.

\response Amen.


\gresetinitiallines1

\chapter{Marian Antiphon}

\rubrics{Solemn tone:}{}

\greannotation{Ant.}
\greannotation{1.}
\gregorioscore{salveregina_solemn}

\rubrics{Simple tone:}{}

\greannotation{5.}
\gregorioscore{salveregina}

\begin{verse}
    \tr{
        Hail, holy Queen, Mother of mercy,\\
        hail, our life, our sweetness, and our hope.\\
        To thee do we cry, the children of Eve;\\
        to thee do we send up our sighs,\\
        mourning and weeping in this valley of tears.\\
        Turn, then, most gracious advocate,\\
        thine eyes of mercy toward us;\\
        and after this our exile, show unto us\\
        the blessed fruit of thy womb, Jesus:\\
        O clement, O loving, O sweet Virgin Mary.

    }
\end{verse}

\startParallel
\versicle  Ora pro nobis sancta Dei Génitrix.
\switchcolumn
\tr{Pray for us, O holy Mother of God.}
\switchcolumn
\response . Ut digni efficiámur promissiónibus Christi.
\switchcolumn
\tr{That we may be made worthy of the promises of Christ.}
\switchcolumn
Orémus.
\switchcolumn
\tr{Let us pray.}
\switchcolumn
Omnípotens sempitérne Deus, qui gloriósae Vírginis Matris Maríae
corpus et ánimam, ut dignum Fílii tui habitáculum éffici mererétur,
Spíritu Sancto cooperánte praeparásti : \dag \  da, ut cujus
commemoratióne laetámur, * ejus pia intercessióne ab
instántibus malis et a morte perpétua liberémur.
Per eúmdem Christum Dóminum nostrum. \response . Amen.
\switchcolumn
\tr{Almighty, everlasting God, who by the co-operation of the Holy Spirit didst prepare the body and soul of the glorious Virgin-Mother Mary to become a dwelling-place meet for thy Son: grant that as we rejoice in her commemoration; so by her fervent intercession we may be delivered from present evils and from everlasting death. Through the same Christ our Lord. Amen.}
\switchcolumn
\versicle  Divínum auxílium máneat semper nobíscum. \response . Amen.
\switchcolumn
\tr{May the divine assistance remain always with us. Amen.}
\stopParallel






\end{document}

