




\gregorioscore{gabc/an--assumpta_est}

\subsection{Psalm 53}

\gresetinitiallines0
\gregorioscore{prima1}

%Deus, in nómine tuo \textbf{sál}vum \textbf{me} fac, * et in virtúte tua \textbf{jú}di\textbf{ca} me.
\startParallel
\setcounter{versecount}{1}
\input gabc/53-7
\stopParallel

\subsection{Psalm 84}

\gregorioscore{prima2.tex}

%Benedixísti, Dómine, \textbf{ter}ram \textbf{tu}am; * avertísti captivi\textbf{tá}tem \textbf{Ja}cob.

\startParallel
\setcounter{versecount}{1}
\input gabc/84-7
\stopParallel


\subsection{Psalm 116}

\gregorioscore{prima3.tex}

%Laudáte Dóminum, \textbf{om}nes \textbf{gen}tes; * laudáte eum, \textbf{om}nes \textbf{pó}puli. 

\startParallel
\setcounter{versecount}{1}
\input gabc/116-7
\switchcolumn
\tr{O praise the Lord, all ye nations: praise him, all ye people. For his mercy is confirmed upon us: and the truth of the Lord remaineth for ever.}
\stopParallel



\setcounter{versecount}{0}


%\section*{Capitulum}
\label{primechapteryear}

\rubrics{(Cant.~6: 9.)}

\startParallel
Quae est ista, quae progréditur quasi auróra consúrgens, \dag\ pulchra ut luna, elécta ut sol, * terríbilis ut castrórum ácies ordináta.
\switchcolumn
\tr{Who is she that cometh forth like the rising dawn, fair as the moon, clear as the sun, terrible as a fenced camp set in battle array? Thanks be to God.}
\switchcolumn
\Rbar. Deo gratias.

\Vbar. Dign\'are me laud\'are te, Virgo sacr\'ata.
\switchcolumn
\tr{Vouchsafe that I may praise thee, O sacred Virgin.}
\switchcolumn
\Rbar. Da mihi virt\'utem contra hostes tuos.
\switchcolumn
\tr{Give me strength against thine enemies.}
\stopParallel

\bigskip


%\section*{Collect}
Kyrie eleison, Christe eleison, Kyrie eleison.

\startParallel
\latin{\Vbar.\ Dómine exáudi oratiónem meam.}
\vern{O Lord, hear my prayer.}
\latin{\Rbar.\ Et clamor meus ad te véniat.}
\vern{And let my cry come unto thee}
\latin{Orémus.}
\vern{Let us pray.}
\stopParallel

\bigskip

\rubrics{Most of the year:}

\startParallel
\latin{Deus, qui virginálem aulam beátae Maríae, in qua habitáres, elígere dignátus es: \dag\ da, quaésumus; ut sua nos defensióne munítos, jucúndos fácias suae interésse commemoratióni.  Qui vivis et regnas cum Deo Patre in unitáte Spíritus Sancti Deus, per ómnia saécula saeculórum.}
\vern{O God, Who wast pleased to choose for thy dwelling-place the maiden palace of Blessed Mary, grant, we beseech thee, that her protection may shield us, and make us glad in her commemoration. Who lives and reigns with God the Father in the unity of the Holy Spirit, one God, world without end. Amen.}
\latin{\Rbar.\ Amen.}
\stopParallel


\startParallel
\latin{\Vbar.\ Dómine exáudi oratiónem meam.}
\vern{O Lord, hear my prayer.}
\latin{\Rbar.\ Et clamor meus ad te véniat.}
\vern{And let my cry come unto thee}
\stopParallel

\ 

\gresetinitiallines0
\gregorioscore{gabc/BenedicamusDomino}

%\Vbar. Benedicámus Dómino.

%\Rbar. Deo grátias.

\ 

\startParallel
%\latin{\Vbar.\ Benedicámus Dómino.}
%\vern{Let us bless the Lord.}
%\latin{\Rbar.\ Deo grátias.}
%\vern{Thanks be to God.}
\latin{\Vbar.\ Fidélium ánimae per misericórdiam Dei requiéscant in pace.}
\vern{May the souls of the faithful departed through the mercy of God rest in peace. Amen.}
\latin{\Rbar.\ Amen.}
\stopParallel


