

\gregorioscore{gabc/an--sancti_dei_omnes--solesmes_1960}

\startParallel
\latin{\versicle Lætamini in Dómino et exsultáte, justi.

    \response Et gloriámini, omnes recti corde.}
\vern{\versicle Be glad in the Lord, and rejoice, ye just.

    \response And be joyful, all ye that are of right heart.}
\latin{Oremus.

    Prótege, Dómine, pópulum tuum, et, Apostolórum tuórum Petri et Pauli et aliórum Apostólorum patrocínio confidéntem, perpétua defensióne consérva.

    Omnes Sancti tui, quǽsumus, Dómine, nos ubíque ádjuvent: ut, dum eórum mérita recólimus, patrocínia sentiámus: et pacem tuam nostris concéde tempóribus, et ab Ecclésia tua cunctam repélle nequítiam; iter, actus et voluntátes nostras et ómnium famulórum tuórum, in salútis tuæ prosperitáte dispóne, benefactóribus nostris sempitérna bona retríbue, et ómnibus fidélibus defúnctis réquiem ætérnam concéde.

    \response Amen.}
\vern{Let us pray.

    Shield, O Lord, Thy people, and ever keep them in Thy care, who put their trust in the pleading of Thine apostles Peter and Paul, and of the other apostles.

    May all Thy saints, we beseech Thee, O Lord, everywhere come to our help, that while we do honor to their merits, we may also enjoy their intercession: grant Thine own peace unto our times, and drive away all wickedness from Thy Church; direct our way, our actions, and our wishes and those of all Thy servants in the way of salvation; to our benefactors render everlasting blessings, and to all the faithful departed grant eternal rest. Through Our Lord Jesus Christ, Thy Son, Who liveth and reigneth with Thee in the unity of the Holy Ghost, God, world without end.

    \response Amen.}
\stopParallel

