\vs Dómine, líbera ánimam meam a lábiis in\textbf{í}quis, * et a lin\textit{gua do}\textbf{ló}sa.

\switchcolumn
\tr{O Lord, deliver my soul from wicked lips, and a deceitful tongue.}
\switchcolumn*
\vs Quid detur tibi, aut quid apponátur \textbf{ti}bi, * ad lin\textit{guam do}\textbf{ló}sam~?

\switchcolumn
\tr{What shall be given to thee, or what shall be added to thee, to a deceitful tongue?}
\switchcolumn*
\vs Sagíttae poténtis a\textbf{cú}tae, * cum carbónibus de\textit{sola}\textbf{tór}iis.

\switchcolumn
\tr{The sharp arrows of the mighty, with coals that lay waste.}
\switchcolumn*
\vs Heu mihi, quia incolátus meus prolongátus est~: \dag\ habitávi cum habitántibus \textbf{Ce}dar~; * 
multum incola fuit á\textit{nima} \textbf{me}a.

\switchcolumn
\tr{Woe is me, that my sojourning is prolonged! I have dwelt with the inhabitants of Cedar: My soul hath been long a sojourner.}
\switchcolumn*
\vs Cum his qui odérunt pacem eram pa\textbf{cí}ficus~; * cum loquébar illis, impugná\textit{bant me} \textbf{gra}tis.

\switchcolumn
\tr{With them that hated peace I was peaceable: when I spoke to them they fought against me without cause.}
\switchcolumn*
\vs Glória Patri et \textbf{Fí}lio * et Spirí\textit{tui} \textbf{San}cto.

\switchcolumn
\tr{Glory be to the Father and to the Son and to the Holy Ghost.}
\switchcolumn*
\vs Sicut erat in princípio, et nunc et \textbf{sem}per * et in sáecula saecu\textit{lórum.} \textbf{A}men.
\switchcolumn
\tr{As it was in the beginning, is now and ever shall be, unto ages of ages. Amen.}

