\latin{Auxílium \textbf{me}um a \textbf{Dó}\textbf{mi}no,~* qui fecit cæ\textit{lum} \textit{et} \textbf{ter}ram.}
\vern{My help is from the Lord, who made heaven and earth.}
\latin{Non det in commotiónem \textbf{pe}dem \textbf{tu}\-um:~* neque dormítet \textit{qui} \textit{cus}\textbf{tó}dit te.}
\vern{May he not suffer thy foot to be moved: neither let him slumber that keepeth thee.}
\latin{Ecce, non dormitábit \textbf{ne}que \textbf{dór}\-\textbf{mi}\-et,~* qui cus\textit{tó}\textit{dit} \textbf{Is}raël.}
\vern{Behold he shall neither slumber nor sleep, that keepeth Israel.}
\latin{Dóminus custódit te, Dóminus pro\-\textbf{téc}\-tio \textbf{tu}a,~* super manum déx\textit{te}\textit{ram} \textbf{tu}am.}
\vern{The Lord is thy keeper, the Lord is thy protection upon thy right hand.}
\latin{Per diem \textbf{sol} non \textbf{u}\textbf{ret} te:~* neque lu\textit{na} \textit{per} \textbf{noc}tem.}
\vern{The sun shall not burn thee by day: nor the moon by night.}
\latin{Dóminus custódit te ab \textbf{om}ni \textbf{ma}lo:~* custódiat ánimam \textit{tu}\textit{am} \textbf{Dó}\-mi\-nus.}
\vern{The Lord keepeth thee from all evil: may the Lord keep thy soul.}
\latin{Dóminus custódiat intróitum tuum, et \textbf{éx}itum \textbf{tu}um:~* ex hoc nunc, et us\textit{que} \textit{in} \textbf{sǽ}culum.}
\vern{May the Lord keep thy coming in and thy going out; from henceforth now and for ever.}
\latin{Glória \textbf{Pa}tri, et \textbf{Fí}\textbf{li}o,~* et Spirí\textit{tu}\textit{i} \textbf{Sanc}to.}
\vern{Glory be \ldots}
\latin{Sicut erat in princípio, et \textbf{nunc}, et \textbf{sem}per,~* et in sǽcula sæcu\textit{ló}\textit{rum}. \textbf{A}men.}


