\vs Auxílium meum a \textbf{Dó}mino, * qui fecit cae\textit{lum et} \textbf{ter}ram.

\switchcolumn
\tr{My help is from the Lord, who made heaven and earth.}
\switchcolumn*
\vs Non det in commotiónem pedem \textbf{tu}um, * neque dormítet \textit{qui cus}\textbf{tó}dit te.

\switchcolumn
\tr{May he not suffer thy foot to be moved: neither let him slumber that keepeth thee.}
\switchcolumn*
\vs Ecce non dormitábit neque \textbf{dór}miet, * qui cus\textit{tódit} \textbf{Is}raël.

\switchcolumn
\tr{Behold he shall neither slumber nor sleep, that keepeth Israel.}
\switchcolumn*
\vs Dóminus custódit te~; Dóminus protéctio \textbf{tu}a, * super manum déx\textit{teram} \textbf{tu}am.

\switchcolumn
\tr{The Lord is thy keeper, the Lord is thy protection upon thy right hand.}
\switchcolumn*
\vs Per diem sol non \textbf{u}ret te, * neque lu\textit{na per} \textbf{no}ctem.

\switchcolumn
\tr{The sun shall not burn thee by day: nor the moon by night.}
\switchcolumn*
\vs Dóminus custódit te ab omni \textbf{ma}lo~; * custódiat ánimam \textit{tuam} \textbf{Dó}minus.

\switchcolumn
\tr{The Lord keepeth thee from all evil: may the Lord keep thy soul.}
\switchcolumn*
\vs Dóminus custódiat introítum tuum et éxitum \textbf{tu}um, * ex hoc nunc et us\textit{que in} \textbf{saé}culum.

\switchcolumn
\tr{May the Lord keep thy coming in and thy going out; from henceforth now and for ever.}
\switchcolumn*
\vs Glória Patri et \textbf{Fí}lio * et Spirí\textit{tui} \textbf{San}cto.

\switchcolumn
\tr{Glory be to the Father, and to the Son, and to the Holy Ghost.}
\switchcolumn*
\vs Sicut erat in princípio, et nunc et \textbf{sem}per * et in sáecula saecu\textit{lórum.} \textbf{A}men.
\switchcolumn
\tr{As it was in the beginning, is now and ever shall be, unto ages of ages. Amen.}

