\vs Stantes erant pedes \textbf{no}stri, * in atriis tu\textit{is, Je}\textbf{rú}salem.

\switchcolumn
\tr{Our feet were standing in thy courts, O Jerusalem.}
\switchcolumn*
\vs Jerúsalem, quae aedificátur ut \textbf{cí}vitas, * cujus participátio ejus \textit{in i}\textbf{dí}psum.

\switchcolumn
\tr{Jerusalem, which is built as a city, which is compact together.}
\switchcolumn*
\vs Illuc enim ascendérunt tribus, tribus \textbf{Dó}mini~: * testimónium Israël, ad confiténdum nó\textit{mini} \textbf{Dó}mini.

\switchcolumn
\tr{For thither did the tribes go up, the tribes of the Lord: the testimony of Israel, to praise the name of the Lord.}
\switchcolumn*
\vs Quia illic sedérunt sedes in ju\textbf{dí}cio, * sedes super \textit{domum} \textbf{Da}vid.

\switchcolumn
\tr{Because their seats have sat in judgment, seats upon the house of David.}
\switchcolumn*
\vs Rogáte quae ad pacem sunt Je\-\textbf{rú}\-sa\-lem, * et abundántia dili\textit{génti}\textbf{bus} te.

\switchcolumn
\tr{Pray ye for the things that are for the peace of Jerusalem: and abundance for them that love thee.}
\switchcolumn*
\vs Fiat pax in virtúte \textbf{tu}a, * et abundántia in túr\textit{ribus} \textbf{tu}is.

\switchcolumn
\tr{Let peace be in thy strength: and abundance in thy towers.}
\switchcolumn*
\vs Propter fratres meos et próximos \textbf{me}os, * loquébar \textit{pacem} \textbf{de} te.

\switchcolumn
\tr{For the sake of my brethren, and of my neighbours, I spoke peace of thee.}
\switchcolumn*
\vs Propter domum Dómini Dei \textbf{no}stri, * quaesívi \textit{bona} \textbf{ti}bi.

\switchcolumn
\tr{Because of the house of the Lord our God, I have sought good things for thee.}
\switchcolumn*
\vs Glória Patri et \textbf{Fí}lio * et Spirí\textit{tui} \textbf{San}cto.

\switchcolumn
\tr{Glory be to the Father, and to the Son, and to the Holy Ghost.}
\switchcolumn*
\vs Sicut erat in princípio, et nunc et \textbf{sem}per * et in sáecula saecu\textit{lórum.} \textbf{A}men.
\switchcolumn
\tr{As it was in the beginning, is now and ever shall be, unto ages of ages. Amen.}






 

 

 


