\latin{Stantes erant \textbf{pe}des \textbf{nos}tri,~\redgreheightstar in átriis tu\textit{is}, \textit{Je}\textbf{rú}salem.}
\vern{Our feet were standing in thy courts, O Jerusalem.}
\latin{Jerúsalem, quæ ædifi\textbf{cá}tur ut \textbf{cí}\-vi\-tas:~\redgreheightstar cujus participátio ejus \textit{in} \textit{id}\textbf{íp}sum.}
\vern{Jerusalem, which is built as a city, which is compact together.}
\latin{Illuc enim ascendérunt tribus, \textbf{tri}\-bus \textbf{Dó}mini:~\redgreheightstar testimónium Israël ad confiténdum nó\textit{mi}\textit{ni} \textbf{Dó}mini.}
\vern{For thither did the tribes go up, the tribes of the Lord: the testimony of Israel, to praise the name of the Lord.}
\latin{Quia illic sedérunt sedes \textbf{in} ju\-\textbf{dí}\-cio,~\redgreheightstar sedes super \textit{do}\textit{mum} \textbf{Da}vid.}
\vern{Because their seats have sat in judgment, seats upon the house of David.}
\latin{Rogáte quæ ad pacem \textbf{sunt} Je\-\textbf{rú}\-sa\-lem:~\redgreheightstar et abundántia dili\textit{gén}\textit{ti}\textbf{bus} te:}
\vern{Pray ye for the things that are for the peace of Jerusalem: and abundance for them that love thee.}
\latin{Fiat pax in vir\textbf{tú}te \textbf{tu}a:~\redgreheightstar et abundántia in túr\textit{ri}\textit{bus} \textbf{tu}is.}
\vern{Let peace be in thy strength: and abundance in thy towers.}
\latin{Propter fratres meos, et \textbf{pró}ximos \textbf{me}os,~\redgreheightstar loquébar \textit{pa}\textit{cem} \textbf{de} te:}
\vern{For the sake of my brethren, and of my neighbours, I spoke peace of thee.}
\latin{Propter domum Dómini, \textbf{De}i \textbf{nos}\-tri,~\redgreheightstar quæsívi \textit{bo}\textit{na} \textbf{ti}bi.}
\vern{Because of the house of the Lord our God, I have sought good things for thee.}
\latin{Glória \textbf{Pa}tri, et \textbf{Fí}lio,~\redgreheightstar et Spirí\textit{tu}\textit{i} \textbf{Sanc}to.}
\vern{Glory be \ldots}
\latin{Sicut erat in princípio, et \textbf{nunc}, et \textbf{sem}per,~\redgreheightstar et in sǽcula sæcu\textit{ló}\textit{rum}. \textbf{A}men.}
