\latin{Lingua mea \textbf{cá}lamus \textbf{scri}bæ:~* velóci\textbf{ter} scri\textbf{bén}tis.}
\vern{My tongue is the pen of a scrivener that writeth swiftly.}
\latin{Speciósus forma præ fíliis hóminum,~† diffúsa est grátia in \textbf{lá}biis \textbf{tu}is:~* proptérea benedíxit te Deus \textbf{in} æ\textbf{tér}num.}
\vern{Thou art beautiful above the sons of men: grace is poured abroad in thy lips; therefore hath God blessed thee for ever.}
\latin{Accíngere gládio tuo super \textbf{fe}mur \textbf{tu}um,~* \textbf{pot}en\textbf{tís}sime.}
\vern{Gird thy sword upon thy thigh, O thou most mighty.}
\latin{Spécie tua et pulchri\textbf{tú}dine \textbf{tu}a:~* inténde, próspere pro\textbf{cé}de, et \textbf{re}gna.}
\vern{With thy comeliness and thy beauty set out, proceed prosperously, and reign.}
\latin{Propter veritátem, et mansuetúdinem, \textbf{et} jus\textbf{tí}tiam:~* et dedúcet te mirabíliter \textbf{déx}tera \textbf{tu}a.}
\vern{Because of truth and meekness and justice: and thy right hand shall conduct thee wonderfully.}
\latin{Sagíttæ tuæ acútæ, pópuli \textbf{sub} te \textbf{ca}dent:~* in corda inimi\textbf{có}rum \textbf{Re}gis.}
\vern{Thy arrows are sharp: under thee shall people fall, into the hearts of the king's enemies.}
\latin{Sedes tua, Deus, in \textbf{sǽ}culum \textbf{sǽ}culi:~* virga directiónis virga \textbf{re}gni \textbf{tu}i.}
\vern{Thy throne, O God, is for ever and ever: the sceptre of thy kingdom is a sceptre of uprightness.}
\latin{Dilexísti justítiam, et odísti in\-\textbf{i}\-qui\-\textbf{tá}\-tem:~* proptérea unxit te, Deus, Deus tuus, óleo lætítiæ præ con\textbf{sór}tibus \textbf{tu}is.}
\vern{Thou hast loved justice, and hated iniquity: therefore God, thy God, hath anointed thee with the oil of gladness above thy fellows.}
\latin{Myrrha, et gutta, et cásia a vestiméntis tuis, a dómi\textbf{bus} e\textbf{búr}neis:~* ex quibus delectavérunt te fíliæ regum in ho\textbf{nó}re \textbf{tu}o.}
\vern{Myrrh and stacte and cassia perfume thy garments, from the ivory houses: out of which the daughters of kings have delighted thee in thy glory.}
\latin{Astitit regína a dextris tuis in vestítu \textbf{de}au\textbf{rá}to:~* circúmdata va\textbf{ri}e\textbf{tá}te.}
\vern{The queen stood on thy right hand, in gilded clothing; surrounded with variety.}
\latin{Audi, fília, et vide, et inclína \textbf{au}rem \textbf{tu}am:~* et oblivíscere pópulum tuum, et domum \textbf{pa}tris \textbf{tu}i.}
\vern{Hearken, O daughter, and see, and incline thy ear: and forget thy people and thy father's house.}
\latin{Et concupíscet Rex de\textbf{có}rem \textbf{tu}um:~* quóniam ipse est Dóminus Deus tuus, et ado\textbf{rá}bunt \textbf{e}um.}
\vern{And the king shall greatly desire thy beauty; for he is the Lord thy God, and him they shall adore.}
\latin{Et fíliæ Tyri \textbf{in} mu\textbf{né}ribus~* vultum tuum deprecabúntur: omnes \textbf{dí}vites \textbf{ple}bis.}
\vern{And the daughters of Tyre with gifts, yea, all the rich among the people, shall entreat thy countenance.}
\latin{Omnis glória ejus fíliæ \textbf{Re}gis ab \textbf{in}tus,~* in fímbriis áureis circumamícta va\textbf{ri}e\textbf{tá}tibus.}
\vern{All the glory of the king's daughter is within in golden borders, clothed round about with varieties.}
\latin{Adducéntur Regi vírgi\textbf{nes} post \textbf{e}am:~* próximæ ejus affe\textbf{rén}tur \textbf{ti}bi.}
\vern{After her shall virgins be brought to the king: her neighbours shall be brought to thee.}
\latin{Afferéntur in lætítia et exsul\textbf{ta}ti\textbf{ó}ne:~* adducéntur in \textbf{tem}plum \textbf{Re}gis.}
\vern{They shall be brought with gladness and rejoicing: they shall be brought into the temple of the king.}
\latin{Pro pátribus tuis nati sunt \textbf{ti}bi \textbf{fí}lii:~* constítues eos príncipes super \textbf{om}nem \textbf{ter}ram.}
\vern{Instead of thy fathers, sons are born to thee: thou shalt make them princes over all the earth.}
\latin{Mémores erunt \textbf{nó}minis \textbf{tu}i:~* in omni generatióne et gene\textbf{ra}ti\textbf{ó}nem.}
\vern{They shall remember thy name throughout all generations.}
\latin{Proptérea pópuli confitebúntur tibi \textbf{in} æ\textbf{tér}num:~* et in \textbf{sǽ}culum \textbf{sǽ}culi.}
\vern{Therefore shall people praise thee for ever; yea, for ever and ever.}
\latin{Glória \textbf{Pa}tri, et \textbf{Fí}lio,~* et Spi\textbf{rí}tui \textbf{Sanc}to.}
\vern{Glory be to the Father \ldots }
\latin{Sicut erat in princípio, et \textbf{nunc}, et \textbf{sem}per,~* et in sǽcula sæcu\textbf{ló}rum. \textbf{A}men.}
