\latin{Proptérea non timébimus dum tur\-\textbf{bá}\-bi\-tur \textbf{ter}ra:~* et transferéntur montes \textbf{in} cor \textbf{ma}ris.}
\vern{Therefore we will not fear, when the earth shall be troubled; and the mountains shall be removed into the heart of the sea.}
\latin{Sonuérunt, et turbátæ sunt \textbf{a}quæ e\textbf{ó}rum:~* conturbáti sunt montes in forti\textbf{tú}dine \textbf{e}jus.}
\vern{Their waters roared and were troubled: the mountains were troubled with his strength.}
\latin{Flúminis ímpetus lætíficat civi\textbf{tá}tem \textbf{De}i:~* sanctificávit tabernáculum \textbf{su}um Al\textbf{tís}simus.}
\vern{The stream of the river maketh the city of God joyful: the most High hath sanctified his own tabernacle.}
\latin{Deus in médio ejus, non \textbf{com}\-mo\-\textbf{vé}\-bi\-tur:~* adjuvábit eam Deus \textbf{ma}ne di\textbf{lú}culo.}
\vern{God is in the midst thereof, it shall not be moved: God will help it in the morning early.}
\latin{Conturbátæ sunt Gentes, et incli\textbf{ná}ta sunt \textbf{re}gna:~* dedit vocem suam, \textbf{mo}ta est \textbf{ter}ra.}
\vern{Nations were troubled, and kingdoms were bowed down: he uttered his voice, the earth trembled.}
\latin{Dóminus vir\textbf{tú}tum no\textbf{bís}cum:~* suscéptor noster \textbf{De}us \textbf{Ja}cob.}
\vern{The Lord of armies is with us: the God of Jacob is our protector.}
\latin{Veníte, et vidéte ópera Dómini,~† quæ pósuit prodígia \textbf{su}per \textbf{ter}ram:~* áuferens bella usque ad \textbf{fi}nem \textbf{ter}ræ.}
\vern{Come and behold ye the works of the Lord: what wonders he hath done upon earth, making wars to cease even to the end of the earth.}
\latin{Arcum cónteret, et con\textbf{frín}get \textbf{ar}\-ma:~* et scuta com\textbf{bú}ret \textbf{i}gni.}
\vern{He shall destroy the bow, and break the weapons: and the shield he shall burn in the fire.}
\latin{Vacáte, et vidéte quóniam \textbf{e}go sum \textbf{De}us:~* exaltábor in Géntibus, et exal\textbf{tá}bor in \textbf{ter}ra.}
\vern{Be still and see that I am God; I will be exalted among the nations, and I will be exalted in the earth.}
\latin{Dóminus vir\textbf{tú}tum no\textbf{bís}cum:~* suscéptor noster \textbf{De}us \textbf{Ja}cob.}
\vern{The Lord of armies is with us: the God of Jacob is our protector.}
\latin{Glória \textbf{Pa}tri, et \textbf{Fí}lio,~* et Spi\textbf{rí}tui \textbf{Sanc}to.}
\vern{Glory be \ldots}
\latin{Sicut erat in princípio, et \textbf{nunc}, et \textbf{sem}per,~* et in sǽcula sæcu\textbf{ló}rum. \textbf{A}men.}
