\latin{Sitívit in te á\textit{ni}\textit{ma} \textbf{me}a,~* quam multiplíciter ti\textit{bi} \textit{ca}\textit{ro} \textbf{me}a.}
\vern{For thee my soul hath thirsted; for thee my flesh, O how many ways!}
\latin{In terra desérta, et ínvia, et inaquósa:~\reddagger sic in sancto appá\textit{ru}\textit{i} \textbf{ti}bi,~* ut vidérem virtútem tuam, et \textit{gló}\textit{ri}\textit{am} \textbf{tu}am.}
\vern{In a desert land, and where there is no way, and no water: so in the sanctuary have I come before thee, to see thy power and thy glory.}
\latin{Quóniam mélior est misericórdia tua \textit{su}\textit{per} \textbf{vi}tas:~* lábia \textit{me}\textit{a} \textit{lau}\textbf{dá}bunt te.}
\vern{For thy mercy is better than lives: thee my lips shall praise.}
\latin{Sic benedícam te in \textit{vi}\textit{ta} \textbf{me}a:~* et in nómine tuo levá\textit{bo} \textit{ma}\textit{nus} \textbf{me}as.}
\vern{Thus will I bless thee all my life long: and in thy name I will lift up my hands.}
\latin{Sicut ádipe et pinguédine repleátur á\textit{ni}\textit{ma} \textbf{me}a:~* et lábiis exsultatiónis lau\textit{dá}\textit{bit} \textit{os} \textbf{me}um.}
\vern{Let my soul be filled as with marrow and fatness: and my mouth shall praise thee with joyful lips.}
\latin{Si memor fui tui super stratum meum,~\reddagger in matutínis medi\textit{tá}\textit{bor} \textbf{in} te:~* quia fuísti \textit{ad}\textit{jú}\textit{tor} \textbf{me}us.}
\vern{If I have remembered thee upon my bed, I will meditate on thee in the morning: Because thou hast been my helper.}
\latin{Et in velaménto alárum tuárum exsultábo,~\reddagger adhǽsit ánima \textit{me}\textit{a} \textbf{post} te:~* me suscépit \textit{déx}\textit{te}\textit{ra} \textbf{tu}a.}
\vern{And I will rejoice under the covert of thy wings: [9] My soul hath stuck close to thee: thy right hand hath received me.}
\latin{Ipsi vero in vanum quæsiérunt ánimam meam,~\reddagger introíbunt in inferi\textit{ó}\textit{ra} \textbf{ter}ræ:~* tradéntur in manus gládii, partes \textit{vúl}\textit{pi}\textit{um} \textbf{e}runt.}
\vern{But they have sought my soul in vain, they shall go into the lower parts of the earth: They shall be delivered into the hands of the sword, they shall be the portions of foxes.}
\latin{Rex vero lætábitur in Deo,~\reddagger laudabúntur omnes qui ju\textit{rant} \textit{in} \textbf{e}o:~* quia obstrúctum est os loquén\textit{ti}\textit{um} \textit{in}\textbf{í}qua.}
\vern{But the king shall rejoice in God, all they shall be praised that swear by him: because the mouth is stopped of them that speak wicked things.}
\latin{Glória Pa\textit{tri}, \textit{et} \textbf{Fí}lio,~* et Spi\textit{rí}\textit{tu}\textit{i} \textbf{Sanc}to.}
\vern{Glory be \ldots}
\latin{Sicut erat in princípio, et \textit{nunc}, \textit{et} \textbf{sem}per,~* et in sǽcula sæ\textit{cu}\textit{ló}\textit{rum}. \textbf{A}men.}
