\latin{Salvávit sibi déx\textit{te}\textit{ra} \textbf{e}jus:~* et bráchi\textit{um} \textit{sanc}\textit{tum} \textbf{e}jus.}
\vern{His right hand hath wrought for him salvation, and his arm is holy.}
\latin{Notum fecit Dóminus salu\textit{tá}\textit{re} \textbf{su}\-um:~* in conspéctu Géntium revelávit jus\textit{títiam} \textbf{su}am.}
\vern{The Lord hath made known his salvation: he hath revealed his justice in the sight of the Gentiles.}
\latin{Recordátus est misericór\textit{di}\textit{æ} \textbf{su}æ,~* et veritátis suæ \textit{dó}\textit{mu}\textit{i} \textbf{Is}raël.}
\vern{He hath remembered his mercy and his truth toward the house of Israel.}
\latin{Vidérunt omnes tér\textit{mi}\textit{ni} \textbf{ter}ræ~* salutá\textit{re} \textit{De}\textit{i} \textbf{nos}tri.}
\vern{All the ends of the earth have seen the salvation of our God.}
\latin{Jubiláte Deo, \textit{om}\textit{nis} \textbf{ter}ra:~* cantáte, et exsul\textit{tá}\textit{te}, \textit{et} \textbf{psál}lite.}
\vern{Sing joyfully to God, all the earth; make melody, rejoice and sing.}
\latin{Psállite Dómino in cíthara, in cíthara et \textit{vo}\textit{ce} \textbf{psal}mi:~* in tubis ductílibus, et vo\textit{ce} \textit{tu}\textit{bæ} \textbf{cór}neæ.}
\vern{Sing praise to the Lord on the harp, on the harp, and with the voice of a psalm: With long trumpets, and sound of cornet.}
\latin{Jubiláte in conspéctu regis Dómini:~† moveátur mare, et pleni\textit{tú}\textit{do} \textbf{e}jus:~* orbis terrárum, et qui há\textit{bi}\textit{tant} \textit{in} \textbf{e}o.}
\vern{Make a joyful noise before the Lord our king: Let the sea be moved and the fulness thereof: the world and they that dwell therein.}
\latin{Flúmina plaudent manu,~† simul montes exsultábunt a con\textit{spéctu} \textbf{Dó}mini:~* quóniam venit ju\textit{dicáre} \textbf{ter}ram.}
\vern{The rivers shall clap their hands, the mountains shall rejoice together at the presence of the Lord: because he cometh to judge the earth.}
\latin{Judicábit orbem terrárum \textit{in} \textit{jus}\textbf{tí}tia,~* et pópulos \textit{in} \textit{æqui}\textbf{tá}te.}
\vern{He shall judge the world with justice, and the people with equity.}
\latin{Glória Pa\textit{tri}, \textit{et} \textbf{Fí}lio,~* et Spi\textit{rí}\textit{tu}\textit{i} \textbf{Sanc}to.}
\vern{Glory be \ldots }
\latin{Sicut erat in princípio, et \textit{nunc}, \textit{et} \textbf{sem}per,~* et in sǽcula sæ\textit{cu}\textit{ló}\textit{rum}. \textbf{A}men.}
