
\startParallel
\vs Et eréxit cornu salútis \textbf{no}bis:~* in domo David, pú\textit{e}\textit{ri} \textbf{su}i.
\switchcolumn
\tr{And hath raised up an horn of salvation to us, in the house of David his servant:}
\switchcolumn*
\vs Sicut locútus est per os sanc\textbf{tó}rum,~* qui a sǽculo sunt, prophe\textit{tá}\textit{rum} \textbf{e}jus:
\switchcolumn
\tr{As he spoke by the mouth of his holy prophets, who are from the beginning:}
\switchcolumn*
\vs Salútem ex inimícis \textbf{nos}tris,~* et de manu ómnium, \textit{qui} \textit{o}\textbf{dé}runt nos.
\switchcolumn
\tr{Salvation from our enemies, and from the hand of all that hate us:}
\switchcolumn*
\vs Ad faciéndam misericórdiam cum pátribus \textbf{nos}tris:~* et memorári testaménti \textit{su}\textit{i} \textbf{sanc}ti.
\switchcolumn
\tr{To perform mercy to our fathers, and to remember his holy testament,}
\switchcolumn*
\vs Jusjurándum, quod jurávit ad Abraham patrem \textbf{nos}trum,~* datú\textit{rum} \textit{se} \textbf{no}bis:
\switchcolumn
\tr{The oath, which he swore to Abraham our father, that he would grant to us,}
\switchcolumn*
\vs Ut sine timóre, de manu inimicórum nostrórum libe\textbf{rá}ti,~* servi\textit{á}\textit{mus} \textbf{il}li.
\switchcolumn
\tr{That being delivered from the hand of our enemies, we may serve him without fear,}
\switchcolumn*
\vs In sanctitáte, et justítia coram \textbf{ip}so,~* ómnibus di\textit{é}\textit{bus} \textbf{nos}tris.
\switchcolumn
\tr{In holiness and justice before him, all our days.}
\switchcolumn*
\vs Et tu, puer, Prophéta Altíssimi vo\textbf{cá}beris:~* præíbis enim ante fáciem Dómini, paráre \textit{vi}\textit{as} \textbf{e}jus:
\switchcolumn
\tr{And thou, child, shalt be called the prophet of the Highest: for thou shalt go before the face of the Lord to prepare his ways:}
\switchcolumn*
\vs Ad dandam sciéntiam salútis plebi \textbf{e}jus:~* in remissiónem peccató\textit{rum} \textit{e}\textbf{ó}rum:
\switchcolumn
\tr{To give knowledge of salvation to his people, unto the remission of their sins:}
\switchcolumn*
\vs Per víscera misericórdiæ Dei \textbf{nos}tri:~* in quibus visitávit nos, óri\textit{ens} \textit{ex} \textbf{al}to:
\switchcolumn
\tr{Through the bowels of the mercy of our God, in which the Orient from on high hath visited us:}
\switchcolumn*
\vs Illumináre his, qui in ténebris, et in umbra mortis \textbf{se}dent:~* ad dirigéndos pedes nostros in \textit{vi}\textit{am} \textbf{pa}cis.
\switchcolumn
\tr{To enlighten them that sit in darkness, and in the shadow of death: to direct our feet into the way of peace.}
\switchcolumn*
\vs Glória Patri, et \textbf{Fí}lio,~* et Spirí\textit{tu}\textit{i} \textbf{Sanc}to.
\switchcolumn
\tr{Glory be to the Father, and to the Son, and to the Holy Ghost.}
\switchcolumn*
\vs Sicut erat in princípio, et nunc, et \textbf{sem}per,~* et in sǽcula sæcu\textit{ló}\textit{rum}. \textbf{A}men.
\switchcolumn
\tr{As it was in the beginning, is now, and ever shall be, and unto ages of ages. Amen.}
\stopParallel
