\latin{Benedícite, Ángeli \textbf{Dó}mini, \textbf{Dó}\-mi\-no:~\redgreheightstar benedícite, \textbf{cæ}li, \textbf{Dó}\-mi\-no.}
\vern{O ye angels of the Lord, bless the Lord: heavens, bless the Lord.}
\latin{Benedícite, aquæ omnes, quæ super \textbf{cæ}los sunt, \textbf{Dó}\-mi\-no:~\redgreheightstar benedícite, omnes virtútes \textbf{Dó}mini, \textbf{Dó}\-mi\-no.}
\vern{O all ye waters that are above the heavens, bless the Lord: O all ye powers of the Lord, bless the Lord.}
\latin{Benedícite, sol et \textbf{lu}na, \textbf{Dó}\-mi\-no:~\redgreheightstar benedícite, stellæ \textbf{cæ}li, \textbf{Dó}\-mi\-no.}
\vern{O ye sun and moon, bless the Lord: stars of heaven, bless the Lord.}
\latin{Benedícite, omnis imber \textbf{et} ros, \textbf{Dó}\-mi\-no:~\redgreheightstar benedícite, omnes spíritus \textbf{De}i, \textbf{Dó}\-mi\-no.}
\vern{O every shower and dew, bless ye the Lord: O all ye spirits of God, bless the Lord.}
\latin{Benedícite, ignis et \textbf{æs}tus, \textbf{Dó}\-mi\-no:~\redgreheightstar benedícite, frigus et \textbf{æs}tus, \textbf{Dó}\-mi\-no.}
\vern{O ye fire and heat, bless the Lord: cold and heat, bless the Lord.}
\latin{Benedícite, rores et pru\textbf{í}na, \textbf{Dó}\-mi\-no:~\redgreheightstar benedícite, gelu et \textbf{fri}gus, \textbf{Dó}\-mi\-no.}
\vern{O ye dews and hoar frosts, bless the Lord: frost and cold, bless the Lord.}
\latin{Benedícite, glácies et \textbf{ni}ves, \textbf{Dó}\-mi\-no:~\redgreheightstar benedícite, noctes et \textbf{di}es, \textbf{Dó}\-mi\-no.}
\vern{O ye ice and snow, bless the Lord: nights and days, bless the Lord.}
\latin{Benedícite, lux et \textbf{té}nebræ, \textbf{Dó}\-mi\-no:~\redgreheightstar benedícite, fúlgura et \textbf{nu}bes, \textbf{Dó}\-mi\-no.}
\vern{O ye light and darkness, bless the Lord: lightnings and clouds, bless the Lord.}
\latin{Benedícat \textbf{ter}ra \textbf{Dó}minum:~\redgreheightstar laudet et superexáltet \textbf{e}um in \textbf{sǽ}cula.}
\vern{O let the earth bless the Lord: let it praise and exalt him above all for ever.}
\latin{Benedícite, montes et \textbf{col}les, \textbf{Dó}\-mi\-no:~\redgreheightstar benedícite, univérsa germinántia in \textbf{ter}ra, \textbf{Dó}\-mi\-no.}
\vern{O ye mountains and hills, bless the Lord: O all ye things that spring up in the earth, bless the Lord.}
\latin{Benedícite, \textbf{fon}tes, \textbf{Dó}\-mi\-no:~\redgreheightstar benedícite, mária et \textbf{flú}mina, \textbf{Dó}\-mi\-no.}
\vern{O ye fountains, bless the Lord: seas and rivers, bless the Lord.}
\latin{Benedícite, cete, et ómnia, quæ movéntur in \textbf{a}quis, \textbf{Dó}\-mi\-no:~\redgreheightstar benedícite, omnes vólucres \textbf{cæ}li, \textbf{Dó}\-mi\-no.}
\vern{O ye whales, and all that move in the waters, bless the Lord: O all ye fowls of the air, bless the Lord.}
\latin{Benedícite, omnes béstiæ et \textbf{pé}cora, \textbf{Dó}\-mi\-no:~\redgreheightstar benedícite, fílii \textbf{hó}minum, \textbf{Dó}\-mi\-no.}
\vern{O all ye beasts and cattle, bless the Lord: sons of men, bless the Lord.}
\latin{Benedícat \textbf{Is}raël \textbf{Dó}minum:~\redgreheightstar laudet et superexáltet \textbf{e}um in \textbf{sǽ}cula.}
\vern{O let Israel bless the Lord: praise and exalt him above all for ever.}
\latin{Benedícite, sacerdótes \textbf{Dó}mini, \textbf{Dó}\-mi\-no:~\redgreheightstar benedícite, servi \textbf{Dó}mini, \textbf{Dó}\-mi\-no.}
\vern{O ye priests of the Lord, bless the Lord: servants of the Lord, bless the Lord.}
\latin{Benedícite, spíritus, et ánimæ jus\-\textbf{tó}\-rum, \textbf{Dó}\-mi\-no:~\redgreheightstar benedícite, sancti, et húmiles \textbf{cor}de, \textbf{Dó}\-mi\-no.}
\vern{O ye spirits and souls of the just, bless the Lord: holy and humble of heart, bless the Lord.}
\latin{Benedícite, Ananía, Azaría, \textbf{Mí}saël, \textbf{Dó}\-mi\-no:~\redgreheightstar laudáte et superexaltáte \textbf{e}um in \textbf{sǽ}cula.}
\vern{O Ananias, Azarias, and Misael, bless ye the Lord: praise and exalt him above all for ever.}
\latin{Benedicámus Patrem et Fílium cum \textbf{Sanc}to \textbf{Spí}ritu:~\redgreheightstar laudémus et superexaltémus \textbf{e}um in \textbf{sǽ}cula.}
\vern{Let us bless the Father and the Son with the Holy Spirit: let us praise and exalt Him above all for ever.}
\latin{Benedíctus es, Dómine, in firma\textbf{mén}to \textbf{cæ}li:~\redgreheightstar et laudábilis, et gloriósus, et superexal\textbf{tá}tus in \textbf{sǽ}cula.}
\vern{Blessed art thou, O Lord in the firmament of heaven: and worthy of praise, and glorious and exalted above all for ever.}
