%\latin{[Deus, in nómine tuo sálvum me fac, * et in virtúte tua júdica me.]}
%\vern{Save me, O God, by thy name, and judge me in thy strength.}
\latin{Deus, exáudi oratió\textit{nem} \textbf{me}am~:~\redgreheightstar áuribus pércipe verba \textit{oris} \textbf{me}i.}
\vern{O God, hear my prayer: give ear to the words of my mouth.}
\latin{Quóniam aliéni insurrexérunt advérsum me,~\reddagger et fortes quæsiérunt áni\textit{mam} \textbf{me}am~:~\redgreheightstar et non proposuérunt Deum ante con\textit{spéctum} \textbf{su}um.}
\vern{For strangers have risen up against me; and the mighty have sought after my soul: and they have not set God before their eyes.}
\latin{Ecce enim Deus ád\textit{ju}\textbf{vat} me~:~\redgreheightstar et Dóminus suscéptor est á\textit{nimæ} \textbf{me}æ.}
\vern{For behold God is my helper: and the Lord is the protector of my soul.}
\latin{Avérte mala inimí\textit{cis} \textbf{me}is~:~\redgreheightstar et in veritáte tua di\textit{spérde} \textbf{il}los.}
\vern{Turn back the evils upon my enemies; and cut them off in thy truth.}
\latin{Voluntárie sacrificá\textit{bo} \textbf{ti}bi,~\redgreheightstar et confitébor nómini tuo, Dómine~: quó\-\textit{ni\-am} \textbf{bo}num est~:}
\vern{I will freely sacrifice to thee, and will give praise, O God, to thy name: because it is good:}
\latin{Quóniam ex omni tribulatióne eri\-\textit{pu}\-\textbf{í}\-sti me~:~\redgreheightstar et super inimícos meos despéxit ó\textit{culus} \textbf{me}us.}
\vern{For thou hast delivered me out of all trouble: and my eye hath looked down upon my enemies.}
\latin{Glória Pátri, \textit{et} \textbf{Fí}lio,~\redgreheightstar et Spirí\textit{tui} \textbf{Sán}cto.}
\vern{Glory be to the Father and to the Son, and to the Holy Ghost.}
\latin{Sicut érat in princípio, et núnc, \textit{et} \textbf{sém}per,~\redgreheightstar et in sǽcula sæcu\textit{lórum}. \textbf{A}men.}
\vern{As it was in the beginning, is now, and ever shall be, world without end.  Amen.}

