%\latin{[Benedixísti, Dómine, terram tuam: * avertísti captivitátem Jacob.]}
%\vern{Lord, thou hast blessed thy land: thou hast turned away the captivity of Jacob.}
\latin{Remisísti iniquitátem plebis \textbf{tu}æ~:~\redgreheightstar operuísti ómnia peccá\textit{ta} \textit{e}\textbf{ó}rum.}
\vern{Thou hast forgiven the iniquity of thy people: thou hast covered all their sins.}
\latin{Mitigásti omnem iram \textbf{tu}am~:~\redgreheightstar avertísti ab ira indignati\textit{ónis} \textbf{tu}æ.}
\vern{Thou hast mitigated all thy anger: thou hast turned away from the wrath of thy indignation.}
\latin{Convérte nos, Deus, salutáris \textbf{no}\-ster~:~\redgreheightstar et avérte iram tu\textit{am} \textit{a} \textbf{no}bis.}
\vern{Convert us, O God our saviour: and turn off thy anger from us.}
\latin{Numquid in ætérnum irascéris \textbf{no}\-bis?~\redgreheightstar aut exténdes iram tuam a generatióne in gene\textit{rati}\textbf{ó}nem?}
\vern{Wilt thou be angry with us for ever: or wilt thou extend thy wrath from generation to generation?}
\latin{Deus, tu convérsus vivifi\textbf{cá}bis nos~:~\redgreheightstar et plebs tua lætá\textit{bitur} \textbf{in} te.}
\vern{Thou wilt turn, O God, and bring us to life: and thy people shall rejoice in thee.}
\latin{Osténde nobis, Dómine, misericórdiam \textbf{tu}am~:~\redgreheightstar et salutáre tu\textit{um} \textit{da} \textbf{no}bis.}
\vern{Shew us, O Lord, thy mercy; and grant us thy salvation.}
\latin{Audiam quid loquátur in me Dóminus \textbf{De}us~:~\redgreheightstar quóniam loquétur pacem in \textit{plebem} \textbf{su}am.}
\vern{I will hear what the Lord God will speak in me: for he will speak peace unto his people:}
\latin{Et super sanctos \textbf{su}os~:~\redgreheightstar et in eos, qui conver\textit{túntur} \textbf{ad} cor.}
\vern{And unto his saints: and unto them that are converted to the heart.}
\latin{Verúmtamen prope timéntes eum salutáre i\textbf{psí}us~:~\redgreheightstar ut inhábitet glória in \textit{terra} \textbf{no}stra.}
\vern{Surely his salvation is near to them that fear him: that glory may dwell in our land.}
\latin{Misericórdia, et véritas obviavérunt \textbf{si}bi~:~\redgreheightstar justítia, et pax \textit{oscu}\textbf{lá}tæ sunt.}
\vern{Mercy and truth have met each other: justice and peace have kissed.}
\latin{Véritas de terra \textbf{or}ta est~:~\redgreheightstar et justítia de cæ\textit{lo} \textit{pro}\textbf{spé}xit.}
\vern{Truth is sprung out of the earth: and justice hath looked down from heaven.}
\latin{Etenim Dóminus dabit beni\-gni\-\textbf{tá}\-tem~:~\redgreheightstar et terra nostra dabit \textit{fructum} \textbf{su}um.}
\vern{For the Lord will give goodness: and our earth shall yield her fruit.}
\latin{Justítia ante eum ambu\textbf{lá}bit~:~\redgreheightstar et ponet in via \textit{gressus} \textbf{su}os.}
\vern{Justice shall walk before him: and shall set his steps in the way.}
\latin{Glória Pátri, et \textbf{Fí}lio,~\redgreheightstar et Spirí\textit{tui} \textbf{Sán}cto.}
\vern{Glory be to the Father and to the Son, and to the Holy Ghost.}
\latin{Sicut érat in princípio, et núnc, et \textbf{sém}per,~\redgreheightstar et in sǽcula sæcu\textit{lórum}. \textbf{A}men.}
\vern{As it was in the beginning, is now, and ever shall be, world without end.  Amen.}
