%\latin{[Deus, in nómine tuo sálvum me fac, * et in virtúte tua júdica me.]}
%\vern{Save me, O God, by thy name, and judge me in thy strength.}
\latin{Deus, exáudi oratiónem \textbf{me}am~:~* áuribus pércipe verba o\textit{ris} \textbf{me}i.}
\vern{O God, hear my prayer: give ear to the words of my mouth.}
\latin{Quóniam aliéni insurrexérunt advérsum me,~† et fortes quæsiérunt ánimam \textbf{me}am~:~* et non proposuérunt Deum ante conspé\textit{ctum} \textbf{su}um.}
\vern{For strangers have risen up against me; and the mighty have sought after my soul: and they have not set God before their eyes.}
\latin{Ecce enim Deus ádju\textbf{vat} me~:~* et Dóminus suscéptor est áni\textit{mæ} \textbf{me}æ.}
\vern{For behold God is my helper: and the Lord is the protector of my soul.}
\latin{Avérte mala inimícis \textbf{me}is~:~* et in veritáte tua dispér\textit{de} \textbf{il}los.}
\vern{Turn back the evils upon my enemies; and cut them off in thy truth.}
\latin{Voluntárie sacrificábo \textbf{ti}bi,~* et confitébor nómini tuo, Dómine~: quóni\textit{am} \textbf{bo}num est~:}
\vern{I will freely sacrifice to thee, and will give praise, O God, to thy name: because it is good:}
\latin{Quóniam ex omni tribulatióne eripu\textbf{í}sti me~:~* et super inimícos meos despéxit ócu\textit{lus} \textbf{me}us.}
\vern{For thou hast delivered me out of all trouble: and my eye hath looked down upon my enemies.}
\latin{Glória Pátri, et \textbf{Fí}lio,~* et Spirítu\textit{i} \textbf{Sán}cto.}
\vern{Glory be to the Father and to the Son, and to the Holy Ghost.}
\latin{Sicut érat in princípio, et núnc, et \textbf{sém}per,~* et in sǽcula sæculó\textit{rum}. \textbf{A}men.}
\vern{As it was in the beginning, is now, and ever shall be, world without end.  Amen.}

