\latin{Deus, exáudi oratiónem \textbf{me}am:~\redgreheightstar áuribus pércipe verba \textit{o}\textit{ris} \textbf{me}i.}
\vern{O God, hear my prayer: give ear to the words of my mouth.
}
\latin{Quóniam aliéni insurrexérunt advérsum me,~\reddagger et fortes quæsiérunt ánimam \textbf{me}am:~\redgreheightstar et non proposuérunt Deum ante con\textit{spéc}\textit{tum} \textbf{su}um.}
\vern{For strangers have risen up against me; and the mighty have sought after my soul: and they have not set God before their eyes.}
\latin{Ecce enim Deus ádju\textbf{vat} me:~\redgreheightstar et Dóminus suscéptor est á\textit{ni}\textit{mæ} \textbf{me}æ.}
\vern{For behold God is my helper: and the Lord is the protector of my soul.}
\latin{Avérte mala inimícis \textbf{me}is:~\redgreheightstar et in veritáte tua dis\textit{pér}\textit{de} \textbf{il}los.}
\vern{Turn back the evils upon my enemies; and cut them off in thy truth.}
\latin{Voluntárie sacrificábo \textbf{ti}bi,~\redgreheightstar et confitébor nómini tuo, Dómine: quón\textit{i}\textit{am} \textbf{bo}num est:}
\vern{I will freely sacrifice to thee, and will give praise, O God, to thy name: because it is good:}
\latin{Quóniam ex omni tribulatióne eripu\textbf{ís}ti me:~\redgreheightstar et super inimícos meos despéxit ó\textit{cu}\textit{lus} \textbf{me}us.}
\vern{For thou hast delivered me out of all trouble: and my eye hath looked down upon my enemies.}
\latin{Glória Patri, et \textbf{Fí}lio,~\redgreheightstar et Spirí\textit{tu}\textit{i} \textbf{Sanc}to.}
\vern{Glory be to the Father, and to the Son and to the Holy Ghost.}
\latin{Sicut erat in princípio, et nunc, et \textbf{sem}per,~\redgreheightstar et in sǽcula sæcu\textit{ló}\textit{rum}. \textbf{A}men.}
\vern{As it was in the beginning, is now, and ever shall be, unto ages of ages. Amen.}
