%\psalmverse{[Benedixísti, Dómine, terram tuam: * avertísti captivitátem Jacob.]}{Lord, thou hast blessed thy land: thou hast turned away the captivity of Jacob.}
\psalmverse{Remisísti iniquitátem \textbf{ple}bis \textbf{tu}æ~:~\redgreheightstar operuísti ómnia pec\textbf{cá}ta e\textbf{ó}rum.}{Thou hast forgiven the iniquity of thy people: thou hast covered all their sins.}
\psalmverse{Mitigásti omnem \textbf{i}ram \textbf{tu}am~:~\redgreheightstar avertísti ab ira indignati\textbf{ó}nis \textbf{tu}æ.}{Thou hast mitigated all thy anger: thou hast turned away from the wrath of thy indignation.}
\psalmverse{Convérte nos, Deus, salu\textbf{tá}ris \textbf{no}\-ster~:~\redgreheightstar et avérte iram \textbf{tu}am a \textbf{no}bis.}{Convert us, O God our saviour: and turn off thy anger from us.}
\psalmverse{Numquid in ætérnum ira\textbf{scé}ris \textbf{no}\-bis?~\redgreheightstar aut exténdes iram tuam a generatióne in gene\textbf{ra}ti\textbf{ó}nem?}{Wilt thou be angry with us for ever: or wilt thou extend thy wrath from generation to generation?}
\psalmverse{Deus, tu convérsus vi\textbf{vi}fi\textbf{cá}bis nos~:~\redgreheightstar et plebs tua læ\textbf{tá}bitur \textbf{in} te.}{Thou wilt turn, O God, and bring us to life: and thy people shall rejoice in thee.}
\psalmverse{Osténde nobis, Dómine, miseri\-\textbf{cór}\-di\-am \textbf{tu}am~:~\redgreheightstar et salutáre \textbf{tu}um da \textbf{no}bis.}{Shew us, O Lord, thy mercy; and grant us thy salvation.}
\psalmverse{Audiam quid loquátur in me \textbf{Dó}\-mi\-nus \textbf{De}us~:~\redgreheightstar quóniam loquétur pacem in \textbf{ple}bem \textbf{su}am.}{I will hear what the Lord God will speak in me: for he will speak peace unto his people:}
\psalmverse{Et super \textbf{san}ctos \textbf{su}os~:~\redgreheightstar et in eos, qui conver\textbf{tún}tur \textbf{ad} cor.}{And unto his saints: and unto them that are converted to the heart.}
\psalmverse{Verúmtamen prope timéntes eum salu\textbf{tá}re i\textbf{psí}us~:~\redgreheightstar ut inhábitet glória in \textbf{ter}ra \textbf{no}stra.}{Surely his salvation is near to them that fear him: that glory may dwell in our land.}
\psalmverse{Misericórdia, et véritas obvia\-\textbf{vé}\-runt \textbf{si}bi~:~\redgreheightstar justítia, et pax \textbf{os}cu\textbf{lá}tæ sunt.}{Mercy and truth have met each other: justice and peace have kissed.}
\psalmverse{Véritas de \textbf{ter}ra \textbf{or}ta est~:~\redgreheightstar et justítia de \textbf{cæ}lo pro\textbf{spé}xit.}{Truth is sprung out of the earth: and justice hath looked down from heaven.}
\psalmverse{Etenim Dóminus dabit be\textbf{ni}\-gni\-\textbf{tá}\-tem~:~\redgreheightstar et terra nostra dabit \textbf{fru}\-ctum \textbf{su}um.}{For the Lord will give goodness: and our earth shall yield her fruit.}
\psalmverse{Justítia ante eum \textbf{am}bu\textbf{lá}bit~:~\redgreheightstar et ponet in via \textbf{gres}sus \textbf{su}os.}{Justice shall walk before him: and shall set his steps in the way.}
\psalmverse{Glória \textbf{Pá}tri, et \textbf{Fí}lio,~\redgreheightstar et Spi\textbf{rí}tui \textbf{Sán}cto.}{Glory be to the Father and to the Son, and to the Holy Ghost.}
\psalmverselast{Sicut érat in princípio, et \textbf{núnc}, et \textbf{sém}per,~\redgreheightstar et in sǽcula sæcu\textbf{ló}rum. \textbf{A}men.}{As it was in the beginning, is now, and ever shall be, world without end.  Amen.}
