\psalmverse{[De profundis clamavi ad te, Domine~:~\redgreheightstar Domine, exáudi vocem meam.]}{Out of the depths I have cried to thee, O Lord: Lord, hear my voice.}
\psalmverse{Fiant aures tuæ \textit{inten}\textbf{dén}tes~:~\redgreheightstar in vocem deprecatiónis meæ.}{Let thy ears be attentive to the voice of my supplication.}
\psalmverse{Si iniquitátes observá\textit{veris}, \textbf{Dó}\-mi\-ne~:~\redgreheightstar Dómine, quis sustinébit?}{If thou, O Lord, wilt mark iniquities: Lord, who shall stand it.}
\psalmverse{Quia apud te propiti\textit{á}\textit{ti}\textbf{o} est~:~\redgreheightstar et propter legem tuam sustínui te, Dómine.}{For with thee there is merciful forgiveness: and by reason of thy
    law, I have waited for thee, O Lord.}
\psalmverse{Sustinuit ánima mea in \textit{verbo} \textbf{e}jus~:~\redgreheightstar sperávit ánima mea in Dómino.}{My soul hath relied on his word: my soul hath hoped in the Lord.}
\psalmverse{A custódia matutína us\textit{que} \textit{ad} \textbf{no}\-ctem~:~\redgreheightstar speret Israël in Dómino.}{From the morning watch even until night, let Israel hope in the Lord.}
\psalmverse{Quia apud Dóminum mi\-\textit{se}\-\textit{ri}\-\textbf{cór}\-dia~:~\redgreheightstar et copiósa apud eum redémptio.}{Because with the Lord there is mercy: and with him plentiful
    redemption.}
\psalmverse{Et ipse réd\textit{imet} \textbf{Is}raël~:~\redgreheightstar ex ómnibus iniquitátibus ejus.}{And he shall redeem Israel from all his iniquities.}
\psalmverse{Glória Pá\textit{tri}, \textit{et} \textbf{Fí}lio,~\redgreheightstar et Spirítui Sáncto.}{Glory be to the Father and to the Son, and to the Holy Ghost.}
\psalmverselast{Sicut érat in princípio, et \textit{núnc}, \textit{et} \textbf{sém}per,~\redgreheightstar et in sǽcula sæculórum. Amen.}{As it was in the beginning, is now, and ever shall be, world without end.  Amen.}
