\latin{[Saepe expugnaverunt me a juventute mea * dicat nunc Israel.]}
\vern{Often have they fought against me from my youth, let Israel now say.}
\latin{Sæpe expugnavérunt me a juven\textit{túte} \textbf{me}a~:~\redgreheightstar étenim non potuérunt mihi.}
\vern{Often have they fought against me from my youth: but they could not prevail over me.}
\latin{Supra dorsum meum fabricavérunt \textit{pecca}\textbf{tó}res~:~\redgreheightstar prolongavérunt iniquitátem suam.}
\vern{The wicked have wrought upon my back: they have lengthened their iniquity.}
\latin{Dóminus justus concídit cervíces \textit{pecca}\textbf{tó}rum~:~\redgreheightstar confundántur et convertántur retrórsum omnes, qui odérunt Sion.}
\vern{The Lord who is just will cut the necks of sinners: Let them all be confounded and turned back that hate Sion.}
\latin{Fiant sicut fœ\textit{num} \textit{te}\textbf{ctó}rum~:~\redgreheightstar quod priúsquam evellátur exáruit~:}
\vern{Let them be as grass upon the tops of houses: which withereth before it be plucked up:}
\latin{De quo non implévit manum su\textit{am} \textit{qui} \textbf{me}tit~:~\redgreheightstar et sinum suum qui manípulos cólligit.}
\vern{Who with the mower filleth not his hand: nor he that gathereth
    sheaves his bosom.}
\latin{Et non dixérunt qui præteríbant~: Benedíctio Dó\textit{mini} \textbf{su}per vos~:~\redgreheightstar benedíximus vobis in nómine Dómini.}
\vern{And they that passed by have not said: The blessing of the Lord be upon you: we have blessed you in the name of the Lord.}
\latin{Glória Pá\textit{tri}, \textit{et} \textbf{Fí}lio,~\redgreheightstar et Spirítui Sáncto.}
\vern{Glory be to the Father and to the Son, and to the Holy Ghost.}
\latin{Sicut érat in princípio, et \textit{núnc}, \textit{et} \textbf{sém}per,~\redgreheightstar et in sǽcula sæculórum. Amen.}
\vern{As it was in the beginning, is now, and ever shall be, world without end.  Amen.}
