\latin{Deus, exáudi orati\textbf{ó}nem \textbf{me}am; * áuribus pércipe verba \textbf{o}ris \textbf{me}i.}
\vern{O God, hear my prayer: give ear to the words of my mouth.}
\latin{Quóniam aliéni insurrexérunt advérsum me, \dag\ et fortes quaesiérunt \textbf{á}nimam \textbf{me}am: * et non proposuérunt Deum ante con\textbf{spé}ctum \textbf{su}um.}
\vern{For strangers have risen up against me; and the mighty have sought after my soul: and they have not set God before their eyes.}
\latin{Ecce enim Deus \textbf{ád}ju\textbf{vat} me, * et Dóminus suscéptor est \textbf{á}nimae \textbf{me}ae.}
\vern{For behold God is my helper: and the Lord is the protector of my soul.}
\latin{Avérte mala ini\textbf{mí}cis \textbf{me}is; * et in veritáte tua dis\textbf{pér}de \textbf{il}los.}
\vern{Turn back the evils upon my enemies; and cut them off in thy truth.}
\latin{Voluntárie sacrifi\textbf{cá}bo \textbf{ti}bi, * et confitébor nómini tuo, Dómine, \textbf{quó}niam \textbf{bo}num est.}
\vern{I will freely sacrifice to thee, and will give praise, O God, to thy name: because it is good:}
\latin{Quóniam ex omni tribulatióne e\-\textbf{ri}\-pu\-\textbf{í}\-sti me, * et super inimícos meos despéxit \textbf{ó}culus \textbf{me}us.}
\vern{For thou hast delivered me out of all trouble: and my eye hath looked down upon my enemies.}
\latin{Glória \textbf{Pa}tri et \textbf{Fí}lio * et Spi\textbf{rí}tui \textbf{San}cto.}
\vern{Glory be to the Father and to the Son and to the Holy Spirit.}
\latin{Sicut erat in princípio, et \textbf{nunc} et \textbf{sem}per * et in sáecula saecu\textbf{ló}rum. \textbf{A}men.}
\vern{As it was in the beginning, is now, and ever shall be, world without end. Amen.}
