\latin{Remisísti iniquitátem \textbf{ple}bis \textbf{tu}ae; * operuísti omnia pec\textbf{cá}ta e\textbf{ó}rum.}
\vern{Thou hast forgiven the iniquity of thy people: thou hast covered all their sins.}
\latin{Mitigásti omnem \textbf{i}ram \textbf{tu}am; * avertísti ab ira indignati\textbf{ó}nis \textbf{tu}ae.}
\vern{Thou hast mitigated all thy anger: thou hast turned away from the wrath of thy indignation.}
\latin{Convérte nos, Deus salu\textbf{tá}ris \textbf{no}ster, * et avérte iram \textbf{tu}am a \textbf{no}bis. }
\vern{Convert us, O God our saviour: and turn off thy anger from us.}
\latin{Numquid in aetérnum ira\textbf{scé}ris \textbf{no}\-bis? * aut exténdes iram tuam a generatióne in gene\textbf{ra}ti\textbf{ó}nem? }
\vern{Wilt thou be angry with us for ever: or wilt thou extend thy wrath from generation to generation?}
\latin{Deus, tu convérsus vi\textbf{vi}fi\textbf{cá}bis nos, * et plebs tua lae\textbf{tá}bitur \textbf{in} te. }
\vern{Thou wilt turn, O God, and bring us to life: and thy people shall rejoice in thee.}
\latin{Osténde nobis, Dómine, miseri\-\textbf{cór}\-diam \textbf{tu}am, * et salutáre \textbf{tu}um da \textbf{no}bis. }
\vern{Shew us, O Lord, thy mercy; and grant us thy salvation.}
\latin{Audiam quid loquátur in me \textbf{Dó}\-mi\-nus \textbf{De}us, * quóniam loquétur pacem in \textbf{ple}bem \textbf{su}am.}
\vern{I will hear what the Lord God will speak in me: for he will speak peace unto his people: }
\latin{Et super \textbf{san}ctos \textbf{su}os, * et in eos qui conver\textbf{tún}tur \textbf{ad} cor. }
\vern{And unto his saints: and unto them that are converted to the heart.}
\latin{Verumtámen prope timéntes eum salu\textbf{tá}re ip\textbf{sí}us, * ut inhábitet glória in \textbf{ter}ra \textbf{no}stra. }
\vern{Surely his salvation is near to them that fear him:that glory may dwell in our land.}
\latin{Misericórdia et véritas obvia\textbf{vé}runt \textbf{si}bi; * justítia et pax \textbf{os}cu\textbf{lá}tae sunt. }
\vern{Mercy and truth have met each other: justice and peace have kissed.}
\latin{Véritas de \textbf{ter}ra \textbf{or}ta est, * et justítia de \textbf{cae}lo pro\textbf{spé}xit. }
\vern{Truth is sprung out of the earth: and justice hath looked down from heaven.}
\latin{Etenim Dóminus dabit be\-\textbf{ni}\-gni\-\textbf{tá}\-tem, * et terra nostra dabit \textbf{fru}ctum \textbf{su}um. }
\vern{For the Lord will give goodness: and our earth shall yield her fruit.}
\latin{Justítia ante eum \textbf{am}bu\textbf{lá}bit, * et ponet in via \textbf{gres}sus \textbf{su}os.}
\vern{Justice shall walk before him: and,shall set his steps in the way.}
\latin{Glória \textbf{Pa}tri et \textbf{Fí}lio * et Spi\textbf{rí}tui \textbf{San}cto.}
\vern{Glory be to the Father and to the Son and to the Holy Spirit.}
\latin{Sicut erat in princípio, et \textbf{nunc} et \textbf{sem}per * et in sáecula saecu\textbf{ló}rum. \textbf{A}men.}
\vern{As it was in the beginning, is now, and ever shall be, world without end. Amen.}
